\section{Main Functionalities}
%What are the main functionalities of the web app? what services does it offer and how it is organized?
% Describe in details what your web application is supposed to do, and what their users will be able to do. Try to be detailed in this section when you describe all the functionalities.

PAINT is a dynamic digital platform designed to bridge the gap between artists, galleries, businesses, and art enthusiasts. 
The web app is built upon the ArtBase database structure. Its functionalities are tailored to the needs of several distinct user roles:

\begin{enumerate}
    \item \textbf{User Management and Role-Based Access:} 
    \begin{itemize}
        \item \textbf{User Registration:} Every user must sign up and log in using secure credentials.
        \item \textbf{Roles:}
        \begin{itemize}
            \item \textbf{Generic Users:} These are individual users who can browse the art collection, view artist profiles, interact with the platform, review, and purchase art.
            \item \textbf{Artists:} These are creators who showcase their work, manage their portfolios.
            \item \textbf{Art Galleries:} Institutions or similar, that promote exhibitions, manage event pages, and collaborate with artists.
            \item \textbf{Business Users:} Companies and commercial entities with enhanced search capabilities.
        \end{itemize}
    \end{itemize}

    \item \textbf{Functionalities for Generic Users:} 
    \begin{itemize}
        \item \textbf{Personalized Homepage:} Automatically generated feeds display recent uploads and updates from followed artists and galleries.
        \item \textbf{Browsing:} Users can search for artist profiles.
        \item \textbf{Social Interactions:} Options to follow artists/galleries and leave reviews art pieces and/or events, to share feedback with the community.
        \item \textbf{Purchasing:} The platform provide a basic e-commerce process and offers a secure payment gateway (PayPal) for purchasing available art pieces.
    \end{itemize}

    \item \textbf{Functionalities for Artists:}
    \begin{itemize}
        \item \textbf{Portfolio Management:} Artists can create and maintain a personal page showcasing their biography, uploaded art pieces, and multimedia albums.
        \item \textbf{Art Upload and Advertisement:} Tools for adding new art pieces with detailed information (title, dimensions, creation date, and description). Artists can mark pieces as available for sale and generate advertisements that update upon purchase.
        \item \textbf{Commission Handling:} An integrated communication channel allows artists to receive, review, and manage commission proposals and inquiries.
        \item \textbf{Profile Monitoring:} Artists can track metrics such as follower counts, sales figures, orders history and user reviews.
    \end{itemize}
    
    \item \textbf{Functionalities for Art Galleries:}
    \begin{itemize}
        \item \textbf{Exhibition \& Event Management:} Galleries can create dedicated pages to promote events. They can upload multimedia content that details exhibitions (e.g., event dates and description, artist participation, and promotional albums).
        \item \textbf{Collaboration with Artists:} Galleries can follow and interact with artists directly to arrange collaborations or invite them to participate in events. Morover, The platform allows galleries to reach both generic and business users.
    \end{itemize}
  
    \item \textbf{Functionalities for Business user:}
    \begin{itemize}
        \item \textbf{Advanced Search \& Filtering:} Business users have access to powerful search tools that let them filter artists by various criteria such as style tags, location, number of published works, and follower counts.
    \end{itemize}
\end{enumerate}

Overall, PAINT is engineered to foster an engaging digital art ecosystem. It not only offers artists and galleries a modern avenue to showcase and sell their work but also provides users with a rich, interactive experience that supports discovery, feedback, and direct commerce.


