\section{Presentation Logic Layer}

%What pages will be present in your project? briefly indicate how your web site will be organized

The website will be divided into the following pages:
\begin{itemize}
    \item Login page: allows the users login to the web application. User must enter their email or username and password for account authentication.
    \item Sign up page: allows the user to register to the web pages. The registration process is divided into 3 different steps/pages where different
    info are requested.
    \begin{itemize}
        \item Personal information page: asks for the user's name, surname, role, brand name, birth date and a recommended profile image.
        \item Address information page: asks for the user's address, city, country and post code.
        \item Account information page: asks to insert the username, email and password for the account.
    \end{itemize}
    \item Homepage: shows the most recent art pieces uploaded by the artists the logged user is following. Also 
    allows user to follow new artists by searching them by username.
    \item Profile settings page: allows user to edit their account info and to access their order history and following 
    lists, which are shown in separate pages.
    \item Artist profile page: is a space managed by an artist where his/her info are shown. Is divided into 3 sections:
    \begin{itemize}
        \item Showcase section: accessed by other users to see a complete list of the artist uploaded art pieces.
        \item Shop section: accessed by other users to potentially buy an art piece being sold by the artist.
        \item Biography section: accessed by other users to get to know more about the artist the profile belongs to.
    \end{itemize}
    \item Art gallery profile page: is similar to the previous described page, but it has only two sections:
    \begin{itemize}
        \item Showcase section: accessed by other users to see the events held in the art gallery.
        \item Biography section: accessed by other users to get to know more about the art gallery the profile belongs 
        to.
    \end{itemize}
    \item Art piece page: displays additional info about an art piece. If it is being sold also allows access to a buy 
    option, which leads to the order page.
    \item Order page: allows the user to buy an art piece. The user will se a summary of the order and will be asked to pay using his PayPal account.
    \item Order history page: shows the user's order history. To simplify the search for a specific order, the user can filter the orders by date or cost. 
\end{itemize}

\subsection{Registration pages (Interface Mokups)}
aggiungere pagina regsitrazione e login una accanto all'altra con descrizione unica per entrambe.
\subsection{Personal information page (Interface Mokup)}
...
\subsection{Address information page (Interface Mokup)}
\subsection{Account information page (Interface Mokup)}
\subsection{Homepage (Interface Mokup)}
\subsection{Profile settings page (Interface Mokup)}
\subsection{Artist profile page (Interface Mokup)}
\subsection{Art gallery profile page (Interface Mokup)}
\subsection{Art piece page (Interface Mokup)}
\subsection{Order page (Interface Mokup)}
\subsection{Order history page (Interface Mokup)}
